---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rladiesgnv

<!-- badges: start -->
<!-- badges: end -->

The goal of rladiesgnv is to encourage a strong and supportive community of R users in Gainesville, FL. This package was created for our meetup in creating packages. You can find the tutorial/presentation [here](https://javirudolph.github.io/RLadies-Gainesville-FL/20190429-Rudolph-packages/apr29presentation.html#1)


## Installation

Actually, you can't install the released version of rladiesgnv from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rladiesgnv")
```

But, the development version is available from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("javirudolph/rladiesgnv")
```
## Example

This is a basic example of the single function this package contains

```{r example}
library(rladiesgnv)
## basic example code
```

```{r}
gimme_color_codes(wantAll = TRUE)
```

```{r}
gimme_color_codes(wantAll = "I'm no fun")
```

Cheers! and enjoy your new packages ~ Javi
